---
title: "Installing snippets"
author: "David Robinson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Installing snippets}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r, echo = FALSE}
library(knitr)
# eval is false so that we're not messing with the installer's snippets
opts_chunk$set(eval = FALSE)
```

You can share your RStudio snippets with others by publishing them as a [GitHub repository](https://github.com/) or a [Gist](https://gist.github.com/).

### Install from GitHub

To share your snippets, create a GitHub repository with one or more `.snippets` file at the top level: see the [dgrtwo/snippets](https://github.com/dgrtwo/snippets) repository for an example. (You can have other files or folders in the repository, such as a `README.md`, and they will be skipped).

Anyone can then install your snippets using the code:

```{r}
library(snippr)
snippets_install_github("dgrtwo/snippets")
```

If you want to install only for one of the languages in the repo, you can use the `language` argument:

```{r}
snippets_install_github("dgrtwo/snippets", language = "r")

# or

snippets_install_github("dgrtwo/snippets", language = "c_cpp")
```

Finally, you can choose to install only a single snippet:

```{r}
snippets_install_github("dgrtwo/snippets", language = "r", name = "S3")
```

### Installing from a GitHub Gist

You can also share one or more snippets as a one-file Gist, such as can be found [here](https://gist.github.com/dgrtwo/ecc6aec8d37af42cdd83). To install that snippet, do:

```{r}
snippets_install_gist("ecc6aec8d37af42cdd83", language = "r")
```

As of now Gist snippets must be a single file (and language), and the language should be specified manually.

### Future Work

* Categories or tags for snippets
* Snippets installed from a package
* Functions to publish to a GitHub repository or Gist
