---
title: "Working with .snippet files"
author: "David Robinson"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r}
library(knitr)
# eval is false so that we're not messing with the installer's snippets
opts_chunk$set(eval = FALSE)
```

While most users will probably need `snippr` only to install published snippets, it provides tools for working directly with `.snippets` files and text.

### Adding and Removing snippets

Suppose we write a snippet for creating an S3 generic:

```{r}
snip <- '${1:funcname} <- function(${2:args}, ...) UseMethod("${1:funcname}")'
```

We can now save that function to our `.snippets` file:

```{r}
library(snippr)
snippet_add("S3", snip)
```

If you restart RStudio you'll reload the snippets, after which you can access the snippet by typing `S3` then hitting Tab. You can replace an existing snippet simply by re-running `snippet_add`. For example, if you want to add curly brackets to the above snippet, do:

```{r}
snip <- '${1:funcname} <- function(${2:args}, ...) {
    UseMethod("${1:funcname}")
}'
snippet_add("S3", snip)
```

You can remove the snippet with:

```{r}
snippet_remove("S3")
```

### Retrieving Snippets

To get a list of the current snippets, do:

```{r}
snippets <- snippets_get()
head(snippets)
```

Or to retrieve a single one:

```{r}
snippet_apply <- snippets_get("apply")
```

You can retrieve snippets for other languages with the `language` argument:

```{r}
html_snippets <- snippets_get(language = "html")
head(html_snippets)
```
